%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Pastry Demi Chef de Partie} % Job title
    {Roux at Skindles} % Organization
    {Taplow, United Kingdom} % Location
    {May. 2022 -- Mar. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Prepared and served various desserts}
        \item {Managed mise-en-place, stock rotation, portion control}
        \item {Maintained hygiene and cleanliness in the kitchen and service areas}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Pastry Commis Chef} % Job title
    {Patisserie Sainte Anne} % Organization
    {London, United Kingdom} % Location
    {Jun. 2019 -- Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Preparation of classic French desserts}
        \item {Appropriate mise-en-place, stock rotation, portion and temperature control}
        \item {Ensuring that the kitchen and service areas, equipment and utensils are always kept clean and tidy}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Pastry Commis Chef} % Job title
    {Hakkasan Group, Yauatcha} % Organization
    {London, United Kingdom} % Location
    {Oct. 2018 -- Mar. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Preparation of desserts, ice cream, macarons in the production kitchen}
        \item {Restaurant service}
        \item {Appropriate mise-en-place, stock rotation, portion and temperature control}
        \vfill\null
        \columnbreak
        \item {Keeping up the highest standards at all times}
        \item {Ensuring that the kitchen and service areas, equipment and utensils are always kept clean and tidy}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Pastry Commis Chef} % Job title
    {Mandarin Oriental Hyde Park} % Organization
    {London, United Kingdom} % Location
    {Mar. 2018 -- Jun. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Preparation and service of the desserts for the Afternoon tea, In Room dining, Rosebery Lounge and banqueting events}
        \item {Ensuring that the highest standards are maintained at all times}
        \item {Ensuring that the kitchen areas, equipment and utensils are always kept clean and tidy}
        \vfill\null
        \columnbreak
        \item {Appropriate mise-en-place, stock rotation and portion control}
        \item {Working with and supporting Demi Chefs, Sous Chef and Executive Pastry Chef}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Pastry Commis Chef} % Job title
    {InterContinental London Park Lane} % Organization
    {London, United Kingdom} % Location
    {Jan. 2018 -- Mar. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Covering Afternoon tea section (preparing mise-en-place, participating in creation of a new menu, checking the stocks)}
        \item {Preparing desserts for banqueting, room service, club lounge, restaurant onsite}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Apprentice Pastry Commis Chef} % Job title
    {InterContinental London Park Lane} % Organization
    {London, United Kingdom} % Location
    {Jul. 2017 -- Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Covering the whole Afternoon tea section (preparing mise-en-place, participating in creating new menu, checking the stocks)}
        \item {Preparing desserts for banqueting, room service, club lounge, restaurant onsite}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Night Porter} % Job title
    {SNOOZEBOX EVENT HOTEL (Catering Services International)} % Organization
    {Cardiff, United Kingdom} % Location
    {Sep. 2015 -- Jan. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working and communication with guests and other departments}
        \item {Dealing with all financial documentation}
        \item {Working with Rezlynx system}
        \item {Keeping reception area clean, setting up for breakfast}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Secretary} % Job title
    {STC LTD} % Organization
    {St. Petersburg, Russia} % Location
    {Aug. 2013 -- Feb. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Providing secretarial and administrative support to all parts of the business}
        \item {Other tasks include covering the reception area, meeting and greeting visitors, answering their queries and dealing with deliveries}
        \item {Making travel and accommodation arrangements for Company Directors and senior managers}
        \item {Handling confidential information in line with the firms data security protocols}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Receptionist} % Job title
    {INTOURIST (4 Star Hotel)} % Organization
    {Krasnodar, Russia} % Location
    {Oct. 2012 -- Jun. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Carrying out all operations concerning guest arrival and departure in compliance with internal procedures, handling reservations}
        \item {Working with other departments (floor staff, technical, etc) and within the front desk team}
        \item {Ensuring that all guest documentation is up-to- date and available and setting up financial documentation}
        \item {Running daily reports}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Interpreter} % Job title
    {PSMA RUS} % Organization
    {Kaluga, Russia} % Location
    {Feb. 2012 -- Aug. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Interpretation}
        \item {Written translation}
        \item {Liaising with all departments on behalf of foreign specialists}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Receptionist} % Job title
    {NIVA (3 Star Hotel)} % Organization
    {Krasnodar, Russia} % Location
    {Jun. 2011 -- Feb. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Carrying out all operations concerning guest arrival and departure, handling reservations}
        \item {Supervising housekeeping team}
        \item {Ensuring that all guest documentation is up-to- date and available setting up financial documentation}
        \item {Running daily reports}
      \end{cvitems}
    }

\end{cventries}
